\documentclass{article}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm}
\title{Improve the Abstract\\English For Academic Purpose - Week3}
\author{Hu Jiyuan}

\begin{document}

\maketitle

\section{Improvement}

More and more attention is being paid on the harm of plastic pollutants for 
human and environment.
Polystyrene (PS) and styrene are toxic compounds used in large quantities in 
the production of fiberglass reinforced polyesters. 
To address this problem, we provides a fast, accurate and sensitive method for 
independent monitoring PS biomarker PGA (phenylglyoxylic acid) in serum and 
urine, and the paper-based probe exhibit a new idea for design portable and 
easy to operate sensing devices combine with smartphone.
We prepared Eu3+ functionalized Sc-based metalorganic frameworks as turn-on 
fluorescent switch for PGA, which has several appealing features including high 
sensitivity (LOD = 4.16 ppb), quick response time (less than 5 s) and broad 
linear range (0.02 mg/mL to 0.5 mg/mL). 
The Eu@MOFs with addition of PGA exhibits distinct enhanced luminescence and 
excellent selectivity that it is not affected by congeneric biomarkers. 
What's more, a paper-based fluorescence probe has been devised, which would 
perform an obvious fluorescence change from navy to red with the variety of PGA 
content.
The practicability of the on-site detection platform for quantitative analysis 
using a colour scanning APP in smartphone has been also demonstrated by coupled 
with our proposed paper based fluorescence probe. 

\section{Origin}

\subsection{Abstract}
The harm of plastic pollutants for human and environment is being paid more and 
more attention. 
% pollutant 污染物 noun [C]
Polystyrene (PS) and styrene are toxic compounds used in large quantities in 
the production of fiberglass reinforced polyesters. 
% polystyrene 聚苯乙烯 noun [U]
% styrene 苯乙烯
% toxic 有毒的
% fiberglass 玻璃纤维 fibreglass
% reinforced 加固 verb [T]
% polyester 聚酯纤维
In this work, a simple method was designed for independent detecting 
polystyrene and styrene biomarker (phenylglyoxylic acid, PGA) in serum and 
urine. 
% serum 血清
% urine 尿
% phenylglyoxylic acid 苯乙醛酸
% acid 酸
We prepared Eu3+ functionalized Sc-based metalorganic frameworks as turn-on 
fluorescent switch for PGA. 
% metalorganic 金属有机物
% fluorescent 荧光的
The distinct enhanced luminescence is observed from the Eu@MOFs with addition 
of PGA. 
% distinct 明显不同的
% luminescence 冷光，发冷光，荧光
The fabricated fluorescent switch has several appealing features including high 
sensitivity (LOD = 4.16 ppb), quick response time (less than 5 s) and broad 
linear range (0.02 mg/mL to 0.5 mg/mL). 
Furthermore, Eu@MOFs exhibits excellent selectivity that it is not affected by
congeneric biomarkers. 
% congeneric 同属的，同类的
More interestingly, a paper-based probe has been devised. 
% devise 发明
The paper-based fluorescence probe would perform an obvious fluorescence change 
from navy to red with the variety of PGA content.
% navy 深蓝色，海军 noun
The practicability of the on-site detection platform for quantitative analysis 
using a colour scanning APP in smartphone has been also demonstrated by coupled 
with our proposed paper based fluorescence probe. 
This work first provides a fast, accurate and sensitive method for independent 
monitoring PS biomarker PGA, and the paper-based probe exhibit a new idea for 
design portable and easy to operate sensing devices combine with smartphone.

\subsection{Keywords}
Turn-on fluorescence,
% 开启荧光？
Polystyrene biomarker,
% 聚苯乙烯生物标记物
Serum and urine sensing,
% 血浆和尿液传感
On-site detection.
% 原位检测

\subsection{Statistics}
Origin: 11 sentences, 232 words.\\
Improvement: 7 sentences, 208 words

\subsection{Source}
Lian, Xiao, Tifang Miao, Xiaoyu Xu, Chi Zhang, and Bing Yan. "Eu3+ 
functionalized Sc-MOFs: Turn-on fluorescent switch for ppb-level biomarker of 
plastic pollutant polystyrene in serum and urine and on-site detection by 
smartphone." Biosensors and Bioelectronics 97 (2017): 299-304.
\\
Url: \url{https://doi.org/10.1016/j.bios.2017.06.018}

\end{document}
